%%% Thesis Introduction --------------------------------------------------
\chapter{Introduction}
\ifpdf
    \graphicspath{{Introduction/IntroductionFigs/PNG/}{Introduction/IntroductionFigs/PDF/}{Introduction/IntroductionFigs/}}
\else
    \graphicspath{{Introduction/IntroductionFigs/EPS/}{Introduction/IntroductionFigs/}}
\fi

It is common for econometricians to study the relationship between dynamics of multiple time series. One of the popular approaches is to look at the coefficient of correlation $R^2$ value and perform ordinary regression analysis. However, \cite{grangernewbold1974} showed that this might give rise to misleading conclusion. Consider the case where $y_t$ and $x_t$ are two independent first order autoregressive processes. It is possible to reject the hypothesis of testing regression coefficients are all zero, i.e., there is significant relation between the two series even though there is none. This phenomenon is called spurious regression. \cite{granger1986} later proposed the concept of cointegration to study long run relationship between multiple series, and he suggested that there might exist a linear combination of multiple integrated time series to be stationary. For instance, for two $I(1)$ processes $y_t$ and $x_t$, they are said to be cointegrated if there exists a constant $\al$ such that $y_t - \al x_t$ is a stationary process. To formally test for existence of cointegration, \cite{englegranger1987} proposed procedures to check whether the residual series is stationary by testing the existence of a unit root.

Since then, cointegration model has been widely used in empirical analysis in various disciplines, including economics, finance and environmental research. In the past few decades, a lot of attention has focused on cointegration models with linear structure. Although linear structure is convenient for practical implementation, it is often too restrictive. In particular, it is common to observe nonlinear responses with some unknown parameters in the context of economics.  A simple example is the class of Douglas-Cobb function used in production theory of macro-economics. The function is given by
\bestar
  y_t = a_t k_t^{\al_1} l_t^{\al_2},
\eestar
where $y_t$ is total production output, $k_t$ is flow of service from capital, $l_t$ is flow of service from labour and $a_t$ is technological shifter. To handle with the nonlinearity, it is common to take logarithm transformation such that standard techniques used in linear cointegration can be applied. However, such method does not apply when the model becomes more complicated. For instance, \cite{arrowcheneryminhassolow1961} later proposed a more generalized production function given by
\be \la{eqn:1:prod}
	y_t = a_t [\de\, k_t^{-\rho} + (1 - \de) \,  l_t^{-\rho}]^{ - 1 / \rho},
\ee
for some constants $\de$ and $\rho$. It is easy to see that (\ref{eqn:1:prod}) is not linear in logarithm and hence ordinary linear cointegration model methodologies do not apply. Another example is the Carbon Kuznets Curve (CKC) used to study the relationship between economic activities and CO$_2$ emission in environmental science. The CKC is given by
\bestar
\log (y_{t}) = \al + \gamma t + \beta_1 \log (x_t) + \beta_2 (\log (x_t))^2,
\eestar
where $y_t$ is per capita GDP and $x_t$ is per capita CO$_2$ emissions. Further examples of nonlinear models can be found in \cite{grangerterasvirta1993}, as well as \cite{terasvirtatjostheimgranger2010}.

These examples show that advanced techniques to analyze nonlinear structure of cointegrating models are necessary. These motivate us to consider the following nonlinear cointegration model
\be \la{eqn:1:model}
y_t = f(x_t) + u_t, \quad t = 1, ..., n,
\ee
where $f$ is a nonlinear function, $x_t$ is a nonstationary time series and $u_t$ is a stochastic error sequence. An important problem immediately arises from the model will be estimation of the nonlinear linked function $f$. There are two popular ways to perform estimation, namely parametric and nonparametric approaches. These two methods are complementary of each other. Parametric method provides data analysts with insights about dynamics of the underlying data generating process. However, it is powerful only when the true model or good approximation of it is correctly specified, and therefore practitioners will run into the risk of mis-specification. For nonparametric approach, it is not necessary to impose a specific mathematical structure on $f$ other than some regularity conditions. Also, it is a useful way to suggest new parametric models and to validate the existing ones.

In the area of nonparametric estimation, one popular estimator adopted in the literature is the Nadaraya-Watson estimator
\bestar
  \widehat{f}(x) = \frac{\sum_{t = 1}^n y_t K_h(x_t - x)}{\sum_{t = 1}^n K_h(x_t - x)},
\eestar
of the linked function $f$. There are extensive research results in the literature concentrated on point-wise estimation and inference of the NW estimator $\widehat{f}$, that is, for any fixed $x \in R$,
\bestar
\widehat{f}(x) \to_P f(x),
\eestar
under different assumptions on the regressor $x_t$. For example, when $x_t$ is stationary time series, \cite{hardlelutkepohlchen1997} provided a comprehensive review of the literature. When $x_t$ is a nonstationary process, \cite{phillipspark1998} studied the model in the context of a random walk. \cite{karlsentjostheim2001} assumed $x_t$ was recurrent Markov chains and \citet[][\citeyear{wangphillips2009}, \citeyear{wangphillips2010b}]{wangphillips2010a} worked with partial sum representations of general linear processes. 

Although there are fruitful results in establishing consistency of nonparametric estimator of $\widehat{f}$ for a particular fixed $x$, results for the uniform convergence of the estimator are scarce. Explicitly, there is little research on showing
\bestar
\sup_{x \in \mathcal{X}} | \widehat{f}(x) - f(x) | \to_P 0,
\eestar
for some $\mathcal{X} \subset R$. Uniform convergence results of $\widehat{f}$ are useful for extending the nonlinear cointegration model in (\ref{eqn:1:model}). As an illustration, we will give a few examples. Firstly, it can be used to estimate volatility function in a regression model with nonlinear nonstationary heteroskedasticity (NNH) error process, which was proposed  by \cite{park2002}. Consider the model
\be \la{eqn:1:coNNH}
y_t = f(x_t) + \si(x_t) u_t, \quad t = 1, ..., n,
\ee
where $\si$ is the volatility function. This model is a generalization of the nonlinear cointegration model (\ref{eqn:1:model}) by incorporating time heterogeneity in the error structure. The conventional kernel estimator is given by
\bestar
\widehat{\si}_n^2(x) = \frac{\sum_{t = 1}^n [y_t  - \widehat{f}(x_t) ]^2 K_h(x_t - x)}{\sum_{t = 1}^n K_h(x_t - x)}.
\eestar
In order to show point-wise consistency, that is, $\widehat{\si}^2_n(x) \to_P \si^2(x)$ for each fixed $x$, we split the estimation error in the following way
\begin{align}
&\widehat{\si}^2(x) - \si^2(x) \no\\
&=\frac{\sum_{t = 1}^n \si^2(x) (u_t^2 - 1) K_h(x_t - x)}{\sum_{t = 1}^n K_h(x_t - x)} + \frac{\sum_{t = 1}^n [\si^2(x_t) - \si^2(x) ] u_t^2 K_h(x_t - x)}{\sum_{t = 1}^n K_h(x_t - x)} \no\\
&+\frac{\sum_{t = 1}^n (f(x_t) - \widehat{f}(x_t))^2 K_h(x_t - x)}{\sum_{t = 1}^n K_h(x_t - x)} + \frac{2\sum_{t = 1}^n \si(x_t) u_t (f(x_t) - \widehat{f}(x_t))  K_h(x_t - x)}{\sum_{t = 1}^n K_h(x_t - x)} \no\\
&:= I_{1n}(x) + I_{2n}(x) + I_{3n}(x) + I_{4n}(x). \no
\end{align}
The uniform convergence result of $\widehat{f}$ can be used to establish the convergence of $I_{3n}(x)$ and $I_{4n}(x)$. Under the assumption that the kernel function has compact support, we have
\bestar
|I_{3n}(x)| \le C  \sup_{y \in \Omega_\ep} | \widehat{f}(y) - f(y)|^2 = o_P(1),
\eestar
for some $\ep > 0$, where $\Omega_\ep = \{y : |y - x | \le \ep, $ where $ x \in R\}$. An extensive exposition of model (\ref{eqn:1:coNNH}) can be found in \cite{wangwang2012}. In addition to estimation of volatility function, uniform convergence of $\widehat{f}$ can also be applied to semi-parametric least square estimation of the class of single index model. This class includes many popular econometric models such as binary choice models, duration models and censored Tobit models, see, e.g., \cite{ichimura1993}. Consider the simple case where the model is given by
\bestar
y_t = f(x_t^T\beta_0) + u_t, \quad t = 1, ..., n,
\eestar
where $x_t$ is a $p \times 1$ vector with nonstationary components and $\beta_0 \in R^p$ is a $p$-dimensional true parameter vector. We denote two objective functions
\bestar
Q_n(\beta) = \sum_{t = 1}^n (y_t - \widehat{f}(x_t^T\beta))^2 \quad \mbox{and} \quad \tilde{Q}_n(\beta) = \sum_{t = 1}^n (y_t - f(x_t^T\beta))^2.
\eestar
The semi-parametric least square estimator of the unknown parameter is defined as $\widehat{\beta}_n = \mbox{arg}\min_{\beta} Q_n(\beta)$. As in \cite{ichimura1993}, the establishment of weak consistency of $\widehat{\beta}_n$ involves proving
\bestar
\sup_{\beta} | Q_n(\beta) - \tilde{Q}_n(\beta)| = o_P(1),
\eestar
which requires uniform convergence of the nonparametric estimator $\widehat{f}$. 

Moreover, the asymptotic distributional theory of $\sup_{x \in \mathcal{X}} |\widehat{f}(x) - f(x)|$ can be used to construct the simultaneous confidence band (SCB) for the estimator $\widehat{f}$ over an interval $\mathcal{X}$. Explicitly, the limit distribution of $\sup_{x \in \mathcal{X}} |\widehat{f}(x) - f(x)|$ is useful for establishing the result
\bestar
 P \big \{ | \widehat{f}(x) -  f(x) |  \le b_n(x, z) \quad  \mbox{for all}\quad  x \in \mathcal{X} \big \}  \to F(z),
\eestar
where $F(z)$ is certain distribution function. Consequently, the $100 (1 - \al)\%$, $\al \in (0,1)$, simultaneous confidence band for $f$ over $\mathcal{X}$ is given by 
\be
\widehat{f}(x) \pm b_n(x, F^{-1}(1 - \al)).
\ee
See, e.g., \cite{zhaowu2008} for more details. 

Last but not least, the uniform asymptotics used to establish the convergence of $\widehat{f}$ can also be applied to unit root testing with nonstationary volatility. When the error structure has a NNH structure instead of the usual i.i.d. formulation, the classical Dickey-Fuller test statistic involves an unknown nuisance parameter $\si$ which is a nonlinear function. This leads to invalid inference on the existence of unit root if ordinary Dickey-Fuller procedure is applied. Using similar techniques to the nonparametric estimator $\widehat{f}$, it is possible to replace the unknown nonlinear function $\si$ with its uniform consistent estimate $\widehat{\si}$. See Chapter \ref{chap:5} for more details.

%Making use of the uniform convergence results, I would propose a unit root testing procedure which can handles with such nuisance parameter. The essential idea of my method is replacing the unknown $\si$ with its consistent estimator $\widehat{\si}$, and hence valid inference of existence of unit root can be obtained. Such method has several advantages over the unit root test with nonstationary volatility proposed by Cavaliere? and Taylor (2009) and xxx (xxx). More details can be found in Section x.x of this thesis.


Motivated by the important applications to analysis of various econometric models, the present thesis aims to establish uniform convergence with rates for the Nadaraya-Watson estimator $\widehat{f}$ with nonstationary regressor $x_t$. The starting point of our development is to show the uniform convergence of two important functionals. To introduce the two functional classes of interest, consider the decomposition of the estimation difference
\begin{align}
	\widehat{f}(x)-f(x) &= \frac{\sum_{t=1}^{n}u_{t}K_{h}(x_{t}-x)}{ \sum_{t=1}^{n}K_{h}(x_{t}-x)}+\frac{\sum_{t=1}^{n}\big[f(x_{t})-f(x)\big] \,K_{h}(x_{t}-x)}{\sum_{t=1}^{n}K_{h}(x_{t}-x)} \no\\
&:= \Theta_{1n}(x)+\Theta_{2n}(x).\no
\end{align}
The second term $\Theta_{2n}(x)$ relates to the bias of the estimation and is very easy to handle with. The asymptotics of $\Theta_{1n}(x)$ involves deriving convergence of the ratio of two random variables, i.e.,
\begin{align}
 \sup_{|x| \le \mathcal{X}} |\Theta_{1n}(x)| &\le \frac{\sup_{|x| \le \mathcal{X}}|\sum_{t=1}^{n}u_{t}K_h(x_{t}-x)|}{\inf_{|x| \le \mathcal{X}}\sum_{t=1}^{n}K_h(x_{t}-x)}  =: \frac{\sup_{|x| \le \mathcal{X}}|S_{1n}(x)|}{\inf_{|x| \le \mathcal{X}}|S_{2n}(x)|}. \no
\end{align}
The numerator $S_{1n}(x)$ is the sample covariance functional while the denominator $S_{2n}(x)$ is the sample average functional. This thesis will systematically derive the upper and lower bounds for $S_{1n}(x)$ and $S_{2n}(x)$ uniformly in $x$ over a slowly expanding set $\mathcal{X}$. While our framework allows for a wide selection of regressor $x_t$, we focus primarily on the case where $x_t$ is nonstationary, and in particular, where $x_t$ is a partial sum of general linear processes and a Harris recurrent Markov chain.

The content of this thesis is divided into seven chapters. This chapter is the introduction. In Chapter \ref{chap:1}, we concern with establishing the uniform convergence of the sample covariance functional $S_{1n}(x)$. We establish a framework for uniform convergence of $S_{1n}(x)$ that allows a wide selection of regressor $x_t$. In Chapter \ref{chap:2}--\ref{chap:3}, we investigate uniform convergence of the sample average functional $S_{2n}(x)$. The main results in Chapter \ref{chap:1}--\ref{chap:3} will be used in Chapter \ref{chap:4}, where we establish the uniform convergence of the nonparametric estimator $\widehat{f}$ of the nonlinear cointegration model (\ref{eqn:1:model}). In Chapter \ref{chap:5}, we demonstrate that the uniform asymptotics we developed can also be applied to unit root testing with nonstationary volatility. Finally, in Chapter \ref{chap:6}, we extend our analysis of cointegration model from nonparametric to parametric estimation of the regression function $f$.

Below, we briefly introduce the content of Chapter \ref{chap:1}--\ref{chap:6} and give a review on the literature. 

Chapter \ref{chap:1} mainly contributes to providing a framework on uniform convergence of the sample covariance functional $S_{1n}(x)$ with broad applicability. In earlier research, the uniform convergence of $S_{1n}(x)$ in the situation that $(u_t, x_t)$ satisfies certain stationary conditions was studied in many articles. \cite{liero1989}, \cite{peligrad1992} and \cite{nzedoukhan2004} considered uniform convergence over a fixed compact set, while \cite{masry1996}, \cite{bosq1998} and \cite{fanyao2003} gave uniform results over an unbounded set. More recently, \cite{hansen2008} provided a set of general uniform consistency results, allowing for stationary strong mixing multivariate data with infinite support, kernels with unbounded support and general bandwidth sequences. However, in comparison to the extensive results where the  $x_t$ comes from a stationary time series data, there is little investigation on uniform convergence of $S_{1n}(x)$ for $x_t$ being a nonstationary time series. In this regard, \cite{gaolitjostheim2011} derived strong and weak consistency results for the case where $x_t$ was a null recurrent Markov chain. \cite{wangwang2012} worked  with partial sum of general linear processes. While the rate of convergence   in \cite{gaolitjostheim2011} was sharp,  they imposed independence between $u_t$ and $x_t$.

We will present a general uniform convergence  result for $S_{1n}(x)$ with independence between the innovation sequence $u_t$ and the regressor series $x_t$ removed. We allow for $u_t$ to be a martingale difference and a wide choice of $x_t$. As a framework,  our  assumption on $x_t$ is only related to the conditional variance of the  martingale. Our high level condition is quite natural and holds true for many interesting and important examples. For stationary time series, we include linear process, stationary mixing time series and iterated random functions.

For nonstationary $x_t$, the conditional variance involved in the high level condition has the same structure as the sample average function $S_{2n}(x)$. In the second part of Chapter \ref{chap:1}, we develop both uniform upper and lower bounds for $S_{2n}(x)$ when the regressor series $x_t$ is a  Harris recurrent Markov chain. The class of Harris recurrent Markov chain is an important class of time series. It includes both stationary and nonstationary data generating process, such as the random walk, and parametric threshold autoregressive (TAR) model. \cite{myklebustkarlsentjostheim2012} also pointed out that null recurrent Markov process is a nonlinear generalization of the linear unit root process.

Chapter \ref{chap:2} continues discussing uniform convergence of the sample average functional $S_{2n}(x)$, under the situation that $x_t$ is a partial sum of linear processes. The general linear process has an essential difference compared to the Harris recurrent Markov chain considered in Chapter \ref{chap:1}, and it is generally more natural to apply for econometric applications. Existing research working on the general linear processes primarily focuses on point-wise asymptotics of $S_{2n}(x)$. For example, \cite{borodinibragimov1995}, \cite{akonom1993} and \cite{phillipspark1998} investigated the particular situation where $x_{k}$ was a partial sum of i.i.d. random variables. \cite{jeganathan2004} studied the asymptotic form of similar functionals when $x_{k}$ was a partial sum of long memory linear processes. \cite{wangphillips2010a} improved the above papers by allowing more general conditions on $x_t$.  \cite{wangphillips2010b} considered point-wise asymptotics of a class of zero energy functionals.  In Chapter \ref{chap:2}, we essentially extend the above point-wise asymptotic results to uniform convergence. It is worth mentioning that the asymptotics of $S_{2n}(x)$ have many statistical applications beyond nonlinear cointegration, such as the nonlinear autoregressive model. See \citet[][\citeyear{wangphillips2012}]{wangphillips2010b} and the reference therein.


Chapter \ref{chap:3} has a similar goal to Chapter \ref{chap:2}, but it establishes the uniform convergence of $S_{2n}(x)$ using a completely different approach and thus provides a better range $\mathcal X$ in which the uniform convergence holds. The new proof involves showing that, under certain conditions and a rich probability space, $S_{2n}(x)$ can be approximated by the local time $L_G(s, x)$ of a Gaussian process $G$ over the real line with certain rates.  We can then establish the uniform lower bound $\inf_{x \in \mathcal X} S_{2n}(x)$ by using some well known properties of the local time process. Applying the local time argument, we essentially obtain the optimal range $\mathcal{X}$ of $x$ in which uniform convergence holds, and therefore improve the results presented in Chapter \ref{chap:2}.

In Chpater \ref{chap:4}, we apply the results established in Chapter \ref{chap:1}--\ref{chap:3} to establish the uniform convergence of the Nadaraya-Watson estimator of the linked function $\widehat{f}$ in a nonlinear cointegration model. Applications of the results established in previous chapters lead to wider choice of regressor series $x_t$, sharp rates of convergence and optimal ranges in which the convergence holds. We also apply our results to establishment of uniform convergence for the local linear estimator. Our results show that, unlike the point-wise situation, the performance of the local linear nonparametric  estimator is superior to that of the Nadaraya-Watson estimator in uniform asymptotics. 

In Chapter \ref{chap:5}, we digress from nonlinear cointegration and demonstrate that our uniform asymptotics results of $S_{1n}(x)$ and $S_{2n}(x)$ can also be applied to unit root testing with nonstationary volatility. There is increasing interest in the investigation of Dickey-Fuller test with time varying error structure, which is  usually referred to as heteroskedasticity. Existing testing algorithms in the literature mostly rely solely on the  time series that generates the volatility, and they do not  take extra explanatory data series into consideration. However, in practice, the forces behind conditional heteroskedasticity is usually driven by another observable variable, and the factor affecting the conditional heteroskedasticity is usually nonstationary. Moreover, although the conditional variance is always non-negative, the explanatory variables usually take both positive and negative values. These facts motivate the necessities in  modelling the volatility by a nonlinear transformation of nonstationary process. Explicitly, it is practicably useful to investigate  the Dickey-Fuller test with  error structure:
\begin{equation} \la{eqn11}
\eta_{t} = \si (x_{t}) u_{t+1}, \quad t = 1,.., n,
\end{equation}
where $x_{t}$ is an observable  nonstationary time series, $\si$ is  a heterogeneity generating function (HGF) and $u_{t}$ forms a martingale innovation sequence. Under such situation, the limiting distribution of the DF statistic involves the HGF $\si$  which is a nuisance parameter. Direct use of standard Dickey-Fuller test critical values (see, e.g., \cite{fuller1996}) will lead to invalid inference of the existence of unit root.

In Chapter \ref{chap:5}, by applying our results on uniform convergence of nonparametric estimators in Chapter \ref{chap:4}, we provide a unit root testing procedure that is capable of handling the non-pivotal quantities appeared in the limiting distribution. The highlight of our method is to use a consistent estimator $\widehat{\si}_n$ in place of the nuisance parameters $\si$. We show that this newly proposed test statistic, based on the Nadaraya-Watson kernel estimators of $\si$, converges weakly to the limiting distribution of the DF-test statistic. Therefore, valid inference of the existence of unit root can be carried out.

A far more complete list of articles in this regard includes: \cite{kimschmidt1993}, \cite{hansenrahbek1998},  \cite{boswijk2001} and later \cite{linglimcaleer2003} considered the well known GARCH process; \cite{hamoritokihisa1997}, \cite{kimleybournenewbold2002}, \cite{cavaliere2005}, \cite{cavalieretaylor2008a} and \cite{beare2008} discussed  the situation that the conditional volatility is modeled as a general deterministic function; \cite{boswijk2005},  \cite{xu2008} and  \citet[][\citeyear{cavalieretaylor2008b}, \citeyear{cavalieretaylor2009}]{cavalieretaylor2007} allowed for volatility process to be stochastic, proposed a unit root test based on kernel estimate of the conditional volatility process and provided a simulation algorithm involving wild bootstrap. Our results in Chapter \ref{chap:5} improve these papers by using external data  explicitly and allowing the dynamics of future volatilities to be affected by current shock.


% ----------------Parametric--------------------------
Finally, in Chapter \ref{chap:6}, we extend our analysis of the cointegration model to parametric estimation. Parametric model is important as it has high forecasting power and could provide empirical researchers with insights about the dynamics of the underlying data generating process. A typical nonlinear parametric cointegrating regression model has the form
 \be y_t&=&
f(x_t, \theta_0)+\,  u_t, \quad t=1,...,n\la {intro.eqn1},
\ee
where  $f:\mathbb{R} \times \mathbb{R}^m \rightarrow \mathbb{R}$ is a known nonlinear function,
$x_t$ and  $u_t$ are regressor and regression errors, and   $\theta_0$ is an $m$-dimensional true parameter vector that lies in the parameter set $\Theta$. Chapter \ref{chap:6} is concerned with nonlinear least squares (NLS) estimation of the unknown parameter $\theta_0 \in \Theta$.

 There are extensive results on the nonlinear parametric regression model when $x_t$ is stationary time series, including \cite{jennrich1969}, \cite{malinvaud1970} and \cite{wu1981}. Also, several authors have studied the model when $x_t$ is a nonstationary time series. Particularly, \cite{parkphillips2001} (PP henceforth) considered $x_t$ to be an integrated, $I(1)$, process. \cite{changparkphillips2001} introduced additional linear time trend term and stationary regressors into model (\ref{intro.eqn1}). Also see \cite{changpark2010} and \cite{shiphillips2010}. More references can be found in Chapter \ref{chap:6}.

Chapter \ref{chap:6} has a similar goal to the previously mentioned papers but offers more general results. Firstly, we establish a general framework for  weak consistency of the NLS estimator, allowing for $x_t$ to be  a  wider class of nonstationary time series. The set of sufficient conditions are easy to apply to various nonstationary regressors, including partial sum of linear processes and recurrent Markov chains. Furthermore, we  provide limit distribution for the NLS estimator. Secondly, in addition to the commonly used martingale innovation structure, our model allows for serial dependence in the equilibrium errors $u_t$ and the innovations driving $x_t$. It is important as our model  permits joint determination of $x_t$ and $y_t$, and hence the system is a time series structural model. Under such situation, the weak consistency and limit distribution of the NLS estimator are also established.


%%% ----------------------------------------------------------------------


% ------------------------------------------------------------
% The application of cointegration model are not limited to business and economics. For instance, in environmental research,

%cointegration models is used to study the   This model is particular related to this thesis as the regressor $x_t$ is GDP, which is commonly agreed that it exhibits nonstationary behavior.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
