\chapter{List of Publications}

{\bf Part I.} Related to this thesis
\begin{enumerate}
\item ``Uniform convergence rates for a class of martingales with application in non-linear co-integrating regression" (with Qiying Wang). Accepted by {\it Bernoulli}, (Chapter 2 and part of Chapter 5 are from this paper).
\item ``Uniform convergence for nonparametric estimators with non-stationary data" (with Qiying Wang). Accepted by {\it Econometric Theory}, (Chapter 3 and part of Chapter 5 are from this paper).
\item ``Nonlinear regressions with nonstationary time series" (with Qiying Wang). Revised and resubmitted to {\it Journal of Econometrics}, (Chapter 7 is from this paper).
\item ``Testing for a unit root with non-stationary volatility" (with Qiying Wang). {\it Manuscript in preparation}, (Chapter 6 is from this paper).
\item ``Uniform approximation to local time with applications in non-linear co-integrating regression" (with Wei Dong Liu and Qiying Wang). {\it Manuscript in preparation}, (Chapter 4 is from this paper).
\end{enumerate}

\medskip
\noindent
{\bf Part II.} Publications of author in other projects
\begin{enumerate}
\item ``Doubly resolvable nearly Kirkman triple systems" (with Julian Abel, Charles Colbourn, Esther Lamken, Chengmin Wang and Jinhua Wang). {\it Journal of Combinatorial Designs}, doi: 10.1002/jcd.21342.
\item ``Existence of GBRDs with block size 4 and BRDs with block size 5" (with Julian Abel, Diana Combe and William Palmer), {\it Designs, Codes and Cryptography}, {\bf 61(3)}, 285--300.
\item ``Existence of doubly near resolvable $(v, 4, 3)$ BIBDs" (with Julian Abel), {\it Australasian Journal of Combinatorics}, {\bf 47}, 109--124.
\end{enumerate}

% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
